\Large\textbf{Preparation GUIDE for Initial-Submission Manuscript}\\~\\ \large\textbf{ Preparation of Papers in Two-Column Format\\ for the ASP-DAC 2014 (\LaTeX2e version)}

### 2013-11-26 exps.tex
updated the graph

Previous results shows that the compiler was only able to find
\textit{d} for HRTCS and Printer/CD2 without relaxing upper bound.
Figure~\ref{fig:graph} shows the accuracy of our result by comparing
differences between programmer specified upper bounds and the actual
bounds obtained from our algorithm.

\begin{figure}[h!]
	\centering
	\begin{tikzpicture}[scale=0.95]
	\begin{groupplot}[group style={group size=2 by 3,
			xlabels at=edge bottom,
			ylabels at=edge left,
		},
			footnotesize,ybar,xtick=data,
			symbolic x
			coords={HRTCS,Motor,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=3.3cm,
			xlabel=Benchmark,
			ylabel style={text width=1.4cm},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(-0.15,-3.9)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\nextgroupplot
			\addplot coordinates {(HRTCS,1)};
			\nextgroupplot
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
			\nextgroupplot
			\addplot coordinates {(Printer/CD1, 1.6)};
			\nextgroupplot
			\addplot coordinates {(Printer/CD2, 1)};
			\addplot coordinates {(Printer/CD2, 1)};
			\nextgroupplot
			\addplot coordinates {(AECS/CD1, 4.25)};
			\nextgroupplot
			\addplot coordinates {(AECS/CD2, 4.25)};
			\addplot coordinates {(AECS/CD2, 4.25)};
	\end{groupplot}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}

>>>>

The previous results show that HRTCS and Printer/CD2 were the only
examples that the compiler was able to find \textit{d} without relaxing
upper bound of \texttt{delay}. Figure~\ref{fig:graph} shows the accuracy
of our result by comparing differences between programmer specified
upper bounds and the actual bounds obtained from our algorithm.

\begin{figure}[h!]
	\centering
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={HRTCS,Printer/CD1,Printer/CD2,AECS/CD1,AECS/CD2},
			height=5cm,
			width=9.5cm,
%      xlabel=Benchmark,
			x tick label style={rotate=45,font=\footnotesize},
			ylabel=Difference factor,
		]
			\addplot coordinates {(HRTCS,1)(Printer/CD1,1.6)(Printer/CD2,1)(AECS/CD1,4.25)(AECS/CD2,4.25)};
			\addplot coordinates {(Printer/CD2, 1)(AECS/CD2, 4.25)};
	\end{axis}
\end{tikzpicture}
\begin{tikzpicture}[scale=0.9]
	\begin{axis}[
			ybar,xtick=data,
			symbolic x
			coords={Motor},
			height=5cm,
			width=9.5cm,
			xlabel=Benchmark,
			xlabel shift={4pt},
			ylabel=Difference factor,
			legend style={
				anchor=north,
				at={(0.45,-0.44)},
				legend columns=-1,
			}
%      nodes near coords
		]
			\addplot coordinates {(Motor, 3.54)};
			\addplot coordinates {(Motor, 3.15)};
			\addplot coordinates {(Motor, 4.46)};
			\addplot coordinates {(Motor, 3.35)};
			\addplot coordinates {(Motor, 2.81)};
			\legend{Delay1,Delay2,Delay3,Delay4,Delay5}
	\end{axis}
\end{tikzpicture}
\caption{Accuracy of the results}
\label{fig:graph}
\end{figure}
